Applying Computational Intelligence Methods for Predicting the Sales of Newly Published Books in a Real Editorial Business Management Environment

### 2016-08-31 paper.tex
changing the meaning of a strange sentence
closing the issue about the flowchart (comment 3 by Rev.3): Closes #48

Once the models and results have been obtained for the whole dataset (Section \ref{sec:experiments}), the same methodology has been applied to some specific cases of publishing companies in order to prove the value of the proposal (Section \ref{sec:example_cases}).
Some specific interpretable models have been created as a final result of the work. The aim is that these can be used as a decision-aid tool for the experts who have to decide on the best print-run quantity for new books to be published, in order to either maximise the benefit, or minimise the costs.

@@

According to Table \ref{tab:all_publishers_no_fs}, it can also be noticed that 
the Linear Regression model outperforms some other complex methods like the 
Random Forest, both in time and in obtained errors. 
Although, Linear Regression is considered as a simple model to build, more 
powerful models can obtain better results in comparable time.

>>>>

Once the models and results have been obtained for the whole dataset (Section \ref{sec:experiments}), the same methodology has been applied to some specific cases of publishing companies in order to prove the value of the proposal (Section \ref{sec:example_cases}).
Some specific interpretable models have been created as a final result of the work. 
%The aim is that these can be used as a decision-aid tool for the experts who have to decide on the best print-run quantity for new books to be published, in order to either maximise the benefit, or minimise the costs.

@@

According to Table \ref{tab:all_publishers_no_fs}, it can also be noticed that 
the Linear Regression model outperforms some other complex methods like the 
Random Forest, both in time and in obtained errors. 
%Although, Linear Regression is considered as a simple model to build, more powerful models can obtain better results in comparable time.  % I change this sentence as its meaning is 'strange'...  [pedro]
Although, Linear Regression is considered as a simple model to build, it can obtain better results than more powerful models in comparable time.
